Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2023-03-08 write-up/fda-recurrent.tex
fixing table for basic simulation, onto delta and checking writeup matches

\begin{table}[!th]
\begin{tabular}{c | p{2cm} p{2cm} p{2cm} p{2cm}}
& \multicolumn{4}{c}{Sampling rate} \\ \cline{2-5}
 & 0.5 & 1 & 2 & 4 \\ \hline
Subsampling variance & - & $9.0 \times 10^{-7}$ & $2.9 \times 10^{-6}$ & $5.8 \times 10^{-6}$  \\
Variance & $7.9 \times 10^{-3}$ & $9.2 \times 10^{-3}$ & $1.0 \times 10^{-2}$ & $1.3 \times 10^{-2}$ \\
Squared Bias & $9.8 \times 10^{-2}$ & $9.5 \times 10^{-2}$ & $9.3 \times 10^{-2}$ & $9.2 \times 10^{-2}$   \\
MISE & $1.1 \times 10^{-1}$ & $1.0 \times 10^{-1}$ & $1.0 \times 10^{-1}$ & $1.0 \times 10^{-1}$ \\ \hline
Avg. runtime (secs) & 317 & 177 & 104 & 68 \\ \hline
Subsampling variance & - & $2.9 \times 10^{-6}$ & $8.9 \times 10^{-6}$ & $2.0 \times 10^{-5}$  \\
Variance & $1.0 \times 10^{-2}$ & $1.3 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.1 \times 10^{-2}$ \\
Squared Bias & $6.9 \times 10^{-2}$ & $6.5 \times 10^{-2}$ & $6.0 \times 10^{-2}$ & $5.4 \times 10^{-2}$   \\
MISE & $7.9 \times 10^{-2}$ & $7.9 \times 10^{-2}$ & $8.0 \times 10^{-2}$ & $8.4 \times 10^{-2}$ \\ \hline
Avg. runtime (secs) & 36 & 23 & 15 & 12 \\ \hline
\end{tabular}
\caption{Mean-integrated squared error, varaince, squared bias, and subsampling variance for $\beta(s)$ given by (1) and (2) respectively.}
\label{tab:mise}
\end{table}

>>>>

\begin{table}[!th]
\begin{tabular}{c | p{2cm} p{2cm} p{2cm} p{2cm} p{2cm}}
& \multicolumn{4}{c}{Sampling rate (per)} \\ \cline{2-6}
 & X1 & X2 & X3 & X4 & X5 \\ \hline
SubS. Variance & - & $1.2 \times 10^{-5}$ & $2.0 \times 10^{-5}$ & $3.5 \times 10^{-5}$ & $8.6 \times 10^{-5}$  \\
Variance & $1.3 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.1 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $3.8 \times 10^{-2}$\\
Squared Bias & $6.3 \times 10^{-2}$ & $6.0 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.7 \times 10^{-2}$   \\
MISE & $7.6 \times 10^{-2}$  & $7.5 \times 10^{-2}$  & $8.2 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $1.1 \times 10^{-1}$ \\
RMISE & -  & 0.99  & 1.08 & 1.16 & 1.39 \\ \hline
Avg. runtime (secs) & 356 & 108 & 51 & 24 & 17 \\ \hline
SubS. variance & - & $2.7 \times 10^{-5}$ & $5.1 \times 10^{-5}$ & $5.7 \times 10^{-5}$ & $7.5 \times 10^{-5}$  \\
Variance & $3.7 \times 10^{-2}$ & $2.7 \times 10^{-2}$ & $2.8 \times 10^{-2}$ & $3.3 \times 10^{-2}$ &  $3.8 \times 10^{-2}$\\
Squared Bias & $3.5 \times 10^{-2}$ & $3.6 \times 10^{-2}$ & $3.4 \times 10^{-2}$ & $3.3 \times 10^{-2}$ & $3.1 \times 10^{-2}$ \\
MISE & $7.2 \times 10^{-2}$ & $6.3 \times 10^{-2}$ & $6.2 \times 10^{-2}$ & $6.6 \times 10^{-2}$ & $6.9 \times 10^{-2}$ \\
RMISE & -  & 0.87  & 0.86 & 0.92 & 0.96 \\ \hline
Avg. runtime (secs) & 1084 & 208 & 93 & 47 & 30 \\ \hline
\end{tabular}
\caption{Mean-integrated squared error, variance, squared bias, and subsampling (SubS) variance for $\beta(s)$ given by (1) and (2) respectively.}
\label{tab:mise}
\end{table}
